They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-05 presentation.qmd
qs functions

@@

cod_round_win_prop_after_x_wins <- tibble(win_streak = 2L:4L) |> 
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_x_wins)
  ) |> 
  unnest(data)
```

```{r}
#| label: cod_round_win_prop_after_x_wins-eval
#| eval: true
cod_round_win_prop_after_x_wins |> 
  transmute(
    `Win Streak` = win_streak,
    `Rounds` = n_rounds,
    `N` = scales::comma(total),
    across(c(prop, expected_poststreak_p), ~scales::percent(.x, accuracy = 0.1)),
    across(
      ends_with('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        round(.x, 2) == 1 ~ '1',
        TRUE ~ as.character(round(.x, 2))
      )
    )
  ) |>
  rename(
    `Actual post-streak win %` = prop,
    `Expected post-streak win %` = expected_poststreak_p,
    `Binom. > p-value` = gt_p_value,
    `Binom. < p-value` = lt_p_value
  ) |> 
  knitr::kable()

@@

save_qs <- function(df, name = deparse(substitute(df))) {
  qs::qsave(df, sprintf('data/%s.qs', name))
}

@@

```{r}
#| label: val_round_win_prop_after_x_wins
#| eval: false
load_qs <- function(name) {
  res <- qs::qread(sprintf('data/%s.qs', name))
  assign(name, value = res, envir = .GlobalEnv)
}
load_qs('val_round_win_prop_after_x_wins_first12r')
load_qs('val_round_win_prop_after_x_wins_second12r')
val_round_win_prop_after_x_wins_first12r |> 
  filter(n > 30) |> 
  mutate(
    gt_signif = gt_p_value <= 0.05
  ) |> 
  ggplot() +
  aes(x = win_streak, y = cumu_w) +
  geom_tile(
    aes(fill = gt_signif)
  ) +
  geom_text(
    aes(label = sprintf(
      '%s | %s\n(%s)',
      scales::percent(prop, accuracy = 1),
      scales::percent(expected_poststreak_p, accuracy = 1),
      scales::comma(total)
      )
    )
  )

@@

```{r}
#| label: cod_round_win_prop_after_xw-eval
#| eval: true
val_round_win_prop_after_xw |> 
  transmute(
    `Win Streak` = win_streak,
    `# of Offensive Wins in First 12 Rounds` = cumu_w,
    `N` = scales::comma(total),
    across(c(prop, expected_poststreak_p), ~scales::percent(.x, accuracy = 0.1)),
    across(
      ends_with('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        round(.x, 2) == 1 ~ '1',
        TRUE ~ as.character(round(.x, 2))
      )
    )
  ) |>
  rename(
    `Actual post-streak win %` = prop,
    `Expected post-streak win %` = expected_poststreak_p,
    `Binom. > p-value` = gt_p_value,
    `Binom. < p-value` = lt_p_value
  ) |> 
  knitr::kable()

@@

::: fragment
First 12 rounds **only**
:::

@@

## Winning a next game given the series state

```{r}

>>>>

```{r}
#| label: qs-funcs
#| eval: true
load_qs <- function(name) {
  res <- qs::qread(sprintf('data/%s.qs', name))
  assign(name, value = res, envir = .GlobalEnv)
}
save_qs <- function(df, name = deparse(substitute(df))) {
  qs::qsave(df, sprintf('data/%s.qs', name))
}

@@

cod_round_win_prop_after_x_wins <- tibble(win_streak = 2L:4L) |> 
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_x_wins)
  ) |> 
  unnest(data)
save_qs(cod_round_win_prop_after_x_wins)
```

```{r}
#| label: cod_round_win_prop_after_x_wins-eval
#| eval: true
load_qs('cod_round_win_prop_after_x_wins')
cod_round_win_prop_after_x_wins |> 
  transmute(
    `Win Streak` = win_streak,
    `Rounds` = n_rounds,
    `N` = scales::comma(total),
    across(c(prop, expected_poststreak_p), ~scales::percent(.x, accuracy = 0.1)),
    across(
      ends_with('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        round(.x, 2) == 1 ~ '1',
        TRUE ~ as.character(round(.x, 2))
      )
    )
  ) |>
  rename(
    `Actual post-streak win %` = prop,
    `Expected post-streak win %` = expected_poststreak_p,
    `Binom. > p-value` = gt_p_value,
    `Binom. < p-value` = lt_p_value
  ) |> 
  knitr::kable()

@@

@@

```{r}
#| label: val_round_win_prop_after_x_wins
#| eval: false
load_qs('val_round_win_prop_after_x_wins_first12r')
load_qs('val_round_win_prop_after_x_wins_second12r')
val_round_win_prop_after_x_wins_first12r |> 
  filter(n > 30) |> 
  mutate(
    gt_signif = gt_p_value <= 0.05
  ) |> 
  ggplot() +
  aes(x = win_streak, y = cumu_w) +
  geom_tile(
    aes(fill = gt_signif)
  ) +
  geom_text(
    aes(label = sprintf(
      '%s | %s\n(%s)',
      scales::percent(prop, accuracy = 1),
      scales::percent(expected_poststreak_p, accuracy = 1),
      scales::comma(total)
      )
    )
  )

@@

```{r}
#| label: cod_round_win_prop_after_xw-eval
#| eval: false
load_qs('val_round_win_prop_after_x_wins_first12r')
val_round_win_prop_after_x_wins_first12r |> 
  transmute(
    `Win Streak` = win_streak,
    `# of Offensive Wins in First 12 Rounds` = cumu_w,
    `N` = scales::comma(total),
    across(c(prop, expected_poststreak_p), ~scales::percent(.x, accuracy = 0.1)),
    across(
      ends_with('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        round(.x, 2) == 1 ~ '1',
        TRUE ~ as.character(round(.x, 2))
      )
    )
  ) |>
  rename(
    `Actual post-streak win %` = prop,
    `Expected post-streak win %` = expected_poststreak_p,
    `Binom. > p-value` = gt_p_value,
    `Binom. < p-value` = lt_p_value
  ) |> 
  knitr::kable()

@@

::: fragment
First 12 rounds **only**

TODO
:::

@@
